Poster: Online RL in the Programmable Dataplane with \approachshort{}

### 2021-10-19 paper/poster-abstract.tex
Camera-ready poster.

\acmYear{2021}
\copyrightyear{2021}
\setcopyright{acmcopyright}
\acmConference{CoNEXT '21}{December 7--10, 2021}{Virtual Event, Germany}
\acmPrice{TBA} % Use the data from your email from ACM rights management
\acmDOI{TBA} % Use the data from your email from ACM rights management
\acmISBN{TBA} % Use the data from your email from ACM rights management

@@

%\vspace{-1em}
\section{Introduction}
\begin{figure}
	\centering
		\includegraphics[keepaspectratio, width=0.8\linewidth]{figures/arch-with-p4}
		\caption{\approachshort{} brings low-latency, online reinforcement learning to SoC- and NPU-based SmartNICs. Classical RL policy methods are the key to making this computationally feasible.\label{fig:netro-arch}}
\end{figure}
\begin{figure}
	\centering
%	\includegraphics[keepaspectratio, width=0.6875\linewidth]{figures/arch-with-p4}
%	\caption{\approachshort{} brings low-latency, online reinforcement learning directly to the dataplane. SoC- and NetFPGA-based SmartNIC devices expose spare compute---making in-situ, asynchronous processing and learning possible alongside P4 dataplanes. Classical RL policy methods are the key to making this computationally feasible.\label{fig:netro-arch}}
	\centering
	\includegraphics[keepaspectratio, width=0.85\linewidth]{figures/coop}
	\caption{Parallel policy execution. A single \emph{controller} delegates RL computation and updates to many \emph{minion} threads, using a shared atomic writeback.\label{fig:single-and-parallel:parallel}}
\end{figure}
Automatic network optimisation, control, and defence are becoming commonplace through data-driven techniques such as RL methods, where every change and its effects improve future decisions made by an agent.
In tandem, P4~\parencite{DBLP:journals/ccr/BosshartDGIMRSTVVW14} and \emph{programmable dataplane} hardware have inspired explosive growth and interest in the research community surrounding in-network computation and offloading.
This ecosystem exposes not only runtime reconfigurable packet processing, but per-packet and per-flow traffic measurement state that can greatly aid network operation~\parencite{DBLP:conf/sosr/GhasemiBR17}.

>>>>

\acmYear{2021}\copyrightyear{2021}
\acmConference[CoNEXT '21]{The 17th International Conference on emerging Networking EXperiments and Technologies}{December 7--10, 2021}{Virtual Event, Germany}
\acmBooktitle{The 17th International Conference on emerging Networking EXperiments and Technologies (CoNEXT '21), December 7--10, 2021, Virtual Event, Germany}
\acmPrice{15.00}
\acmDOI{10.1145/3485983.3493345}
\acmISBN{978-1-4503-9098-9/21/12}

@@

%\vspace{-1em}
\section{Introduction}
\begin{figure}
	\centering
		\includegraphics[keepaspectratio, width=0.8\linewidth]{figures/arch-with-p4}
		\caption{\approachshort{} brings low-latency, online reinforcement learning to SoC- and NPU-based SmartNICs. Classical RL policy methods are the key to making this computationally feasible.\label{fig:netro-arch}}
\end{figure}
\begin{figure}
	\centering
%	\includegraphics[keepaspectratio, width=0.6875\linewidth]{figures/arch-with-p4}
%	\caption{\approachshort{} brings low-latency, online reinforcement learning directly to the dataplane. SoC- and NetFPGA-based SmartNIC devices expose spare compute---making in-situ, asynchronous processing and learning possible alongside P4 dataplanes. Classical RL policy methods are the key to making this computationally feasible.\label{fig:netro-arch}}
	\centering
	\includegraphics[keepaspectratio, width=0.8\linewidth]{figures/coop}
	\caption{Parallel policy execution. A single \emph{controller} delegates RL computation and updates to many \emph{minion} threads, using a shared atomic writeback.\label{fig:single-and-parallel:parallel}}
\end{figure}
Automatic network optimisation, control, and defence are becoming commonplace through data-driven techniques such as RL methods, where every change and its effects improve future decisions made by an agent.
In tandem, P4~\parencite{DBLP:journals/ccr/BosshartDGIMRSTVVW14} and \emph{programmable dataplane} hardware have inspired explosive growth and interest in the research community surrounding in-network computation and offloading.
This ecosystem exposes not only runtime reconfigurable packet processing, but per-packet and per-flow traffic measurement state that can greatly aid network operation~\parencite{DBLP:conf/sosr/GhasemiBR17}.
